%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Piotr Tarasiewicz} \\ \vspace{1pt}
    \small +48 506 046 433 $|$ \href{mailto:taras.piotr@gmail.com}{\underline{taras.piotr@gmail.com}} $|$ 
    \href{https://linkedin.com/in/taraspiotr}{\underline{linkedin.com/in/taraspiotr}} $|$
    \href{https://github.com/taraspiotr}{\underline{github.com/taraspiotr}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College London}{London, UK}
      {Machine Learning MSc}{Sep. 2020 -- Sep. 2021 (projected)}
      \resumeItemListStart
        \resumeItem{Courses in Deep Learning, Reinforcement Learning (DeepMind), Kernel Methods (Gatsby Unit), Probabilistic and Unsupervised Learning (Gatsby Unit), Approximate Inference (Gatsby Unit), Supervised Learning, Natural Language Processing.}
      \resumeItemListEnd
    \resumeSubheading
      {Warsaw University of Technology}{Warsaw, Poland}
      {Bachelor of Science in Robotics}{Oct. 2014 -- March 2018}
      \resumeItemListStart
        \resumeItem{Graduated with summa cum laude distinction, (Cumulative Grade 4,84/5).}
        \resumeItem{Three-time winner of the Chancellor's Scholarship for Academic Excellence.}
        \resumeItem{Thesis title: Applications of artificial intelligence for games with imperfect information.}
      \resumeItemListEnd
    \resumeSubheading
      {XIV High School}{Warsaw, Poland}
      {Class with experimental maths profile}{Sep. 2011 -- April 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Scientist}{March 2020 -- Sep. 2020}
      {AdColony Inc.}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Tech stack: Python, PyTorch, BigQuery, SQL, Airflow.}
        \resumeItem{Build machine learning models for users CTR and IPM prediction for one of the largest ad networks.}
        \resumeItem{Design and prototype probabilistic model for market landscape prediction in RTB auctions.}
        \resumeItem{Buil a reinforcement learning model to optimize the trade off between exploitation and exploration of the new supply and demand.}
    \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{April 2018 -- March 2020}
      {deepsense.ai (CodiLime Group)}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Tech stack: Python, PyTorch, SQL, Tensorflow (Tensorpack), scikit-learn, lightgbm.}
    \resumeItemListEnd
    \resumeSubSubheading
    {Data Scientist III}{Oct. 2018 - March 2020}
      \resumeItemListStart
        \resumeItem{Technical leader of a project that developed model predicting over 30\% of out of stock situations for one of the biggest e-commerce company in Poland.}
        \resumeItem{Member of a team that created RL Agent (A3C algorithm) for stock trading.}
        \resumeItem{Created an algorithm for matching mobile advertisers with publishers (reach of more than 1.5 billion users worldwide).}
        \resumeItem{Created Deep Learning model for annotating damaged products on the images.}
      \resumeItemListEnd
      
    \resumeSubSubheading
    {Data Scientist II}{April 2018 - Sep. 2018}
        \resumeItemListStart
            \resumeItem{Co-author of a winning solution for Mapping Challenge that achieved 0.95 mAP score on segmenting satellite images.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{June 2016 -- March 2017}
      {Robert Bosch GmbH}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Development of web and windows applications in .NET using NX (Siemens PLM Software) API to automate engineering work.}
        \resumeItem{I've reduced running time of an algorithm to remove sensitive design information from 3D models by 80\% (in C++).}
        \resumeItem{Started a project for AgroBot - an autonomous robot to monitor greenhouses (using Python and ROS).}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{February 2016}
      {AB-Micro}{Warsaw, Poland}
      \resumeItemListStart
        \resumeItem{Programming a game on a PLC controller as a part of the project for Automaticon: International Fair for Industrial Automation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Auxiliary Tasks in Reinforcement Learning}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Try to understand when it's better to know than to learn to know (use additional signal as an input or as an auxiliary tasks) across reinforcement learning tasks.}
            \resumeItem{Introduce a hybrid approach with progressive nets (additional signal both as an input and output).}
            \resumeItem{Use Soft Actor Criting and PPO algorithms as baselines.}
            \resumeItem{Conducted in cooperation with RL researchers from University of Warsaw and Jagiellonian University in Poland.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Universcan}}{Nov. 2015 -- June 2018}
          \resumeItemListStart
            \resumeItem{Back-end Developer and Webmaster and the Warsaw University of Technology coordinator in a social project that reached tens of thousands of young people by creating a free mobile app for sharing academic events in Warsaw. Working with Facebook Graph API to automatically index and categorize all academic events in Warsaw.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, Julia, C/C++} \\
     \textbf{Frameworks}{: PyTorch, Tensorflow} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, Google Cloud Platform, Linux} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, xgboost, scikit-learn, lightgbm, SciPy}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
